# Example Chart: 2016 General Election, Trump v. Clinton

You can use **pollstR** and **ggplot2** to creates charts similar to those the Huffpost Pollster website.
The Huffpost Pollster combines polls with similar questions into "charts".
This is the current Huffpost Pollster chart for the [2016 General Election: Clinton vs. Trump](http://elections.huffingtonpost.com/pollster/2016-general-election-trump-vs-clinton).

<script src="http://elections.huffingtonpost.com/pollster/2016-general-election-trump-vs-clinton/embed.js"></script>

We will create a similar chart using R with date up to `r Sys.Date()`, when this vignette was built.
This example will use the following packages,
```{r message=FALSE}
library("ggplot2")
library("dplyr")
library("tidyr")
```

The first thing to do is find the slug for the chart of interest, which we will need to pull data from the API.
The slug 2016 General Election results chart is `2016-general-election-trump-vs-clinton`.
In general, the chart slug the last segment of the chart's URL: `http://elections.huffingtonpost.com/pollster/2016-general-election-trump-vs-clinton`.
```{r}
slug <- "2016-general-election-trump-vs-clinton"
```

We will need two things for this plot: the poll results, and Pollster's smoothed estimates which aggregate the polls.
To get the polls associated with a specific chart, we use `pollster_chart_tbl()`. 
While the `pollster_polls()` function returns polls, and has a `chart` argument, it is now deprecated and unreliable, 
When a poll had questions associated with multiple charts, the API would randomly assign a chart value.
However, the `chart_tbl()` function correctly returns the poll data in a Pollster chart (see the [API docs](http://elections.huffingtonpost.com/pollster/api#chart-csv)).
```{r elec_2016_polls_notrun, eval=FALSE}
elec_2016_polls <- pollster_chart_data(slug)
```
```{r, elec_2016_polls_save, eval=FALSE, warning=FALSE, include=FALSE}
# run this interactively to create the data file
elec_2016_polls <- pollster_chart_data(slug)
save(elec_2016_polls, file = "vignettes/children/elec_2016_polls.Rdata")
```
```{r elec_2016_polls_hide, include=FALSE}
load("elec_2016_polls.Rdata")
```
```{r elec_2016_polls_glimpse}
glimpse(elec_2016_polls)
```
It will be easier to deal with this data if it is tidy, with each row a (date, pollster, subpop, choice) combination, 
and variables for the poll result, and sample size.
Also, since each poll has a start and end date, calculate the median date for each poll so we have a single date to 
use in the analysis.
```{r tidy_elec_2016_polls}
elec_2016_polls_tidy <-
  elec_2016_polls %>%
  gather(choice, value, one_of("Clinton", "Trump", "Undecided", "Other")) %>%
  mutate(date = start_date +
           difftime(end_date, start_date, units = "days") / 2) %>%
  filter(!is.na(value))
glimpse(elec_2016_polls_tidy)
```

Now we can plot these polls. There are four choices (Trump, Clinton, Other, and Undecided).
In order to use a more semantically meaningful color scheme than the default color palettes in 
**ggplot2** or other categorical palettes, we will use the color palette used by the [Sunlight Foundation](http://sunlightfoundation.com/blog/2014/03/12/datavizguide/),
in which Republicans are red, Democrats are blue, and independents are green.
```{r elect_2016_polls_plot1}
choice_colours <- c("Trump" = "#9A3E25", "Clinton" = "#156B90", "Other" = "#708259", "Undecided" = "#978F80")
scale_colour_elec_2016 <- function(...) {
  scale_colour_manual(values = choice_colours)
}
scale_fill_elec_2016 <- function(...) {
  scale_fill_manual(values = choice_colours)
}

plot_elec_2016_1 <-
  ggplot(elec_2016_polls_tidy, aes(x = date, y = value, colour = choice)) +
  geom_point() +
  scale_colour_elec_2016() +
  theme_minimal()
plot_elec_2016_1
```
We can add our own smoothers through the data, such as a loess smoother:
```{r plot_elec_2016_loess}
plot_elec_2016_1 +
  geom_smooth(aes(fill = choice), method = "loess") +
  scale_fill_elec_2016()
```

The smoothed poll averages that Huffpost Pollster uses in their charts are available 
through `pollster_chart`,
```{r elec_2016_est_notrun, eval = FALSE}
elec_2016_est <- pollster_chart(slug)
```
```{r elec_2016_est_save, eval=FALSE, include=FALSE}
# run this interactively to create the data file
elec_2016_est <- pollster_chart(slug)
save(elec_2016_est, file = "vignettes/children/elec_2016_est.Rdata")
```
```{r elec_2016_est_hide, include = FALSE}
load("elec_2016_est.Rdata")
```
```{r elec_2016_est}
glimpse(elec_2016_est)
```
The object returned by `pollster_chart` contains elements with metadata about the chart (topic, state, ...),
and two data frames: `estimates` (current estimate), `estimates_by_date` (historical estimates).
However, the API does not return the uncertainty around the estimates (nor the different levels of smoothing available through their website):
```{r plot_elec_2016_2}
plot_elec_2016_1 +
  geom_line(data = elec_2016_est[["estimates_by_date"]],
            mapping = aes(x = date, y = value, colour = choice))
```
