---
title: "PollstR Usage"
author: "Jeffrey Arnold"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{PollstR Usage}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document provides a few examples that use the **pollstR** package.
```{r message=FALSE}
library("pollstR")
library("ggplot2")
library("dplyr")
library("tidyr")
library("purrr")
```

# Produce a Plot of Chart

The **pollstR** package can be used to reproduce plots in the charts.
This will use the Donald Trump favorable rating as the example.
This chart has the slug [donald-trump-favorable-rating](http://elections.huffingtonpost.com/pollster/donald-trump-favorable-rating)
```{r message=FALSE}
slug <- "donald-trump-favorable-rating"
polls <- pollster_charts_polls(slug)[["content"]]
trendlines <- pollster_charts_trendlines(slug)[["content"]]
```
Plot the points for each response (Favorable, Unfavorable, and Undecided) and fit a loess smoother through them:
```{r}
.data <- gather(polls, response, value,
                Favorable, Unfavorable, Undecided) %>%
  mutate(value = if_else(is.na(value), 0, value))
ggplot() +
  geom_point(data = .data,
             aes(x = end_date, y = value, color = response),
             alpha = 0.5) +
  geom_smooth(data = .data, method = "loess", se = FALSE,
              aes(x = end_date, y = value, color = response))
  
```
Plot the points with the Pollster trendlines:
```{r}
ggplot() +
  geom_point(data = .data,
             mapping = aes(x = end_date, y = value, color = response),
             alpha = 0.5) +
  geom_line(data = trendlines,
            mapping = aes(x = date, y = value, color = label), size = 1.5)
```

For each of the subpopulations (Likely Voter, Registered Voters, Adults), plot the favorability rating:
```{r}
ggplot(data = filter(.data, response == "Favorable"),
       mapping = aes(x = end_date, y = value, color = sample_subpopulation)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "loess", se = FALSE)
```


# Questions

An example of a single question item:
```{r}
questions <- pollster_questions()
questions$content$items[[1]]
```

# Charts

An example of a single chart item:
```{r}
charts <- pollster_charts()
charts$content$items[[1]]
```

# Polls

An example of a single poll item:
```{r}
polls <- pollster_polls()
polls$content$items[[1]]
```

# Tags

Get all available tags for use as the `tag` parameter with charts, polls, and questions:
```{r}
map_chr(pollster_tags()$content, "slug")
```

