# Example: Obama's Job Approval Rating

This section shows how to use ``pollstr`` to create a chart similar to those displayed on the Huffpost Pollster website.
I'll use Obama's job approval rating in this example.

The slug or name of the chart is ``obama-job-approval``, which is derived from the chart's URL , http://elections.huffingtonpost.com/pollster/obama-job-approval.
I'll focus on approval in 2013 in order to reduce the time necessary to run this code.
```{r}
slug <- "obama-job-approval"
start_date <- as.Date("2013-1-1")
end_date <- as.Date("2014-1-1")
```
For the plot, I'll need both Pollster's model estimates and opinion poll estimates.
I get the Pollster model estimates using ``polster_chart``,
```{r}
chart <- pollstr_chart(slug)
estimates <- chart[["estimates_by_date"]]

estimates <- estimates[estimates$date >= start_date 
                       & estimates$date < end_date, ]
```
and the opinion poll results,
```{r}
polls <- pollstr_polls(chart = slug, 
                        after = start_date, 
                        before = end_date,
                        max_pages = 1000000)
```
Note that in ``polster_poll`` I set the ``max_pages`` argument to a very large number in order to download all the polls available.
This may take several minutes.

Before continuing, we will need to clean up the opinion poll data.
First, only keep results from national subpopulations ("Adults", "Likely Voters", "Registered Voters").
This will drop subpopulations like Republicans, Democrats, and Independents.
```{r}
questions <-
    subset(polls[["questions"]],
           chart == slug
           & subpopulation %in% c("Adults", "Likely Voters", "Registered Voters"))

```
Second, I will need to recode the choices into three categories, "Approve", "Disapprove", and "Undecided".
```{r}
approvalcat <- c("Approve" = "Approve",
                 "Disapprove" = "Disapprove",
                 "Undecided" = "Undecided",
                 "Neither" = "Undecided",
                 "Refused" = NA,
                 "Neutral" = "Undecided",
                 "Strongly Approve" = "Approve",
                 "Somewhat Approve" = "Approve", 
                 "Somewhat Disapprove" = "Disapprove",
                 "Strongly Disapprove" = "Disapprove")

questions2 <-
    (questions
     %.% mutate(choice = plyr::revalue(choice, approvalcat))
     %.% group_by(id, subpopulation, choice)
     %.% summarise(value = sum(value)))
```
Now merge the question data with the poll metadata,
```{r}
polldata <- merge(polls$polls, questions2, by = "id")
```

Now, I can plot the opinion poll results along with the Huffpost Pollster trend estimates,
```{r obama-favorable-chart-2}
(ggplot()
 + geom_point(data = polldata,
              mapping = aes(y = value, x = end_date, color = choice),
              alpha = 0.3)
 + geom_line(data = estimates,
             mapping = aes(y = value, x = date, color = choice))
 + scale_x_date("date")
 + scale_color_manual(values = c("Approve" = "black", 
                                 "Disapprove" = "red", 
                                 "Undecided" = "blue"))
 )


```

<!--  LocalWords:  Huffpost API Huffington CRAN github devtools str
 -->
<!--  LocalWords:  devools jrnold ggplot obama url aes favorability
 -->
<!--  LocalWords:  Bararck
 -->
